\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\title{Internship Assessment Task}
\date{}
\author{}

\begin{document}
\maketitle
\vspace{-2em}

Build a simple full-stack application using React (Frontend) and Python/FastAPI (Backend) that interacts with a private Google Sheet.

\section*{Requirements}

\subsection*{Backend (FastAPI)}
\begin{enumerate}[topsep=2pt, itemsep=2pt]
    \item Connect to a private Google Sheet using a Google Service Account.
    \item Implement complete CRUD functionality with the following endpoints:
    \begin{itemize}[topsep=2pt, itemsep=2pt]
        \item \texttt{GET /records} -- Fetch all records.
        \item \texttt{GET /record/\{id\}} -- Fetch a specific record.
        \item \texttt{POST /record} -- Create a new record.
        \item \texttt{PUT /record/\{id\}} -- Update an existing record.
        \item \texttt{DELETE /record/\{id\}} -- Delete a record.
    \end{itemize}
    \item Credentials must be stored securely and not hardcoded.
    \item Implement proper validation and error handling.
\end{enumerate}

\subsection*{Frontend (React)}
Create a simple UI to:
\begin{enumerate}[topsep=2pt, itemsep=2pt]
    \item Display records from the Google Sheet in a table.
    \item Create new records.
    \item Edit existing records.
    \item Delete records.
    \item Handle loading and error states appropriately.
\end{enumerate}

\subsection*{Google Sheet Structure}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{ID} & \textbf{Name} & \textbf{Email} & \textbf{Department} \\
\hline
\end{tabular}
\end{center}

The ID field should uniquely identify each record and be used for update and delete operations.

\section*{Evaluation Criteria}
\begin{itemize}[topsep=2pt, itemsep=2pt]
    \item React and FastAPI fundamentals.
    \item API design and integration.
    \item Secure handling of credentials.
    \item Code quality and project structure.
    \item Error handling and validation.
    \item Documentation.
\end{itemize}

\section*{System Design Question}
Design a scalable architecture for this application if:
\begin{itemize}[topsep=2pt, itemsep=2pt]
    \item The Google Sheet contains 1 million+ records.
    \item The application serves 10,000 daily active users.
\end{itemize}

Describe:
\begin{itemize}[topsep=2pt, itemsep=2pt]
    \item Proposed architecture
    \item Database choice
    \item Caching strategy
    \item Authentication and security
    \item Deployment approach
    \item Limitations of Google Sheets and how you would overcome them
\end{itemize}

\end{document}